---
title: "LectureAssignment"
author: "Ramin Farhanian"
date: "July 19, 2017"
output: 
  html_document:
    keep_md: TRUE
---

# Introduction
 The lecture assignment is about analyzing a typical time series data. We will download the data, calculate the log returns, calculating volatility measure, and calculating volatility for the entire series using three different decay factors.
 
 
# Required Packages
The required packages should be installed once before the rest of the code executes. 
```{r}
installLibrariesOnDemand <- function (packages)
{
  cat("Installing required libraries on demand:", packages , "\n")
  new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
  if(length(new.packages)) install.packages(new.packages)
  cat("Missing libraries installation is complete.", "\n")
}
installLibrariesOnDemand(c("tseries", "fpp"))
library(tseries)
library(fpp)
```
 
# Download time series data
```{r}
ausbeerts <- ts(ausbeer, frequency = 4, start = 1956)
plot(ausbeerts)
```
# Calculate the log returns
```{r}
ausbeerLogTs <- log(ausbeerts)
plot(ausbeerLogTs)
ausbeerts2 <- window(ausbeerLogTs, start=1979, end=1989)
ts.plot(ausbeerts2)
ausBeerReturn <- log(lag(ausbeerts2)) - log(ausbeerts2)
ts.plot(ausBeerReturn)
```

# Calculate Volatility measure and volatility measure with a continuous lookback window
```{r}
ausBeerVol <- sd(ausBeerReturn)*sqrt(40)* 100

Vol <- function(d, logrets) {
    var = 0
    lam = 0
    varlist <- c()
    for(r in logrets) {
      lam = lam * (1- 1/d) + 1
      var = (1- 1/lam)*var + (1/lam)*r^2
      varlist <- c(varlist,var)
    }
    sqrt(varlist)
}
volest <- Vol(10, ausBeerReturn)
volest2 <- Vol(30, ausBeerReturn)
volest3 <- Vol(100, ausBeerReturn)
```

# Plot the results with a volatility curve overlay
```{r}
ts.plot(volest, gpars=list(ylab="Volatility"))
lines(volest2,  col="red")
lines(volest3,  col="blue")
```


